### 2021-03-23 Figures/BRMS_Metric_PPCA.Rmd
Edits

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=17, fig.width=17}

@@

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
              size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
              geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits")

@@

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = PC2, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC2, y = Visits),
  size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits")

Specialization_PC1 <- ggplot(spe_1[[1]], aes(x = PC1, y = (estimate__))) + geom_point(data = data_analysis2,aes(x = PC1, y = d),
                      size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')")

Specialization_PC2 <- ggplot(spe_2[[1]], aes(x = PC2, y = (estimate__))) + geom_point(data = data_analysis2,aes(x = PC2, y = d),
                      size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')")

>>>>

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=13, fig.width=17}

@@

Visits_PC1 <- ggplot(ce_1[[1]], aes(x = PC1, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC1, y = Visits),
       size = 1.5, alpha=0.9) + geom_line(colour="darkblue",size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1,fill="darkblue") + ylab("Number of visits")+ ggtitle("A")

@@

Visits_PC2 <- ggplot(ce_2[[1]], aes(x = PC2, y = (estimate__+1))) + geom_point(data = data_analysis2,aes(x = PC2, y = Visits),
  size = 1.2, alpha=0.9) + geom_line(size=1.2) + ylim(0,quantile(data_analysis2$Visits, 0.95)) +theme_ms()+
  geom_ribbon(aes(ymin=(lower__+1), ymax=(upper__+1)), linetype=2, alpha=0.1) + ylab("Number of visits") + ggtitle("B")

Specialization_PC1 <- ggplot(spe_1[[1]], aes(x = PC1, y = (estimate__))) + geom_point(data = data_analysis2,aes(x = PC1, y = d),
                      size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')") + ggtitle("C")

Specialization_PC2 <- ggplot(spe_2[[1]], aes(x = PC2, y = (estimate__))) + geom_point(data = data_analysis2,aes(x = PC2, y = d),
                      size = 1.2, alpha=0.9) + geom_line(size=1.2)  +theme_ms()+
                      geom_ribbon(aes(ymin=(lower__), ymax=(upper__)), linetype=2, alpha=0.1) + ylab("Specilization (d')") + ggtitle("D")

### 2021-03-23 Figures/Figure_Brms_Model_Bees.Rmd
Edits

setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github

result <- readRDS("result_Tukey_model.RDS")

ggplot(result, aes(x = .value, y = contrast,  fill=contrast)) +
  stat_eye( point_interval = median_qi,
            .width = c(0.66, 0.95),alpha=0.7) +theme_ms() +theme(legend.position = "none")+geom_vline(xintercept=0,linetype="dashed") + ylab("Pairwise comparisons") + xlab("Marginal mean difference")

>>>>

#SAVE MODEL 1
setwd("~/Dropbox/PhD/R") #DROPBOX, files too large for github
model_bee_families <- readRDS("model_bee_families.RDS")
d_5_1 <- readRDS("data_model_just_bees.RDS")

##############

#############
#PLOT MODEL 1 NON APIS
#############
ce_1 <- conditional_effects(model_bee_families, effects = "Clusters:bee_family",points=T) 
#change colnames in model output to use same aesthetics
#if not gg seems to don't like it
colnames(ce_1[[1]])[4] <- "a"
colnames(ce_1[[1]])[10] <- "Interaction"
ce_1[[1]][10]<- ce_1[[1]][10]+1

ggplot(ce_1[[1]], aes(x = Clusters, y = Interaction, colour = as.factor(bee_family), group = 
                        as.factor(bee_family))) +
  geom_point(size = 2.4, position = position_dodge(width = 0.8), alpha=1) +
  theme_ms()+ ylab("Nº of visits per plant taxa") + xlab("Plant reproductive groups")+
  geom_point(data = d_5_1,aes(x = Clusters, y = (Interaction+1)),size = 1.2,shape=21, position = position_jitterdodge(dodge.width = 0.8, jitter.width = 0.2), alpha=0.3)+
  geom_errorbar(data=ce_1[[1]],mapping=aes(x=Clusters, ymin=lower__, ymax=upper__,colour = as.factor(bee_family), group = 
                                             as.factor(bee_family)), width=.6,alpha=0.8, size = 0.9,position = position_dodge(width = 0.8)) +ylim(0,200)+
  scale_color_manual("Bee families",values=c("#E69F00","#D55E00", "#287DAB", "#009E73", "#A7473A",  "black"))
